Title

### 2019-05-01 paper_notes.Rmd
added paper cancelled pics

---
output:
  bookdown::pdf_document2:
    toc: false
    keep_tex: false
    fig_caption: yes
title: "Title"
author: Author
bibliography: "references.bib"
csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
---

@@

# PARAGRAPH NAME

>>>>

---
output:
  bookdown::pdf_document2:
    toc: false
    keep_tex: false
    fig_caption: yes
title: "Title"
author: Author
bibliography: "references.bib"
csl: apa.csl # by default: Chicago style
header-includes:
- \usepackage{float}
- \usepackage{multirow}
- \usepackage{xcolor} 
---

@@

```
\newcommand{\rocco}[1]{\textcolor{red}{{Rocco:}#1}} <!-- command to appear in pdf -->
<!-- command not to appear in pdf -->
# PARAGRAPH NAME
